Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-08 kappa.tex
Add references on glacial history.

In the northern sector of the ice sheet, at least four glaciations have been
identified \mref. The two older episodes, often referred to as Reid and
pre-Reid, are older than the last glacial cycle \mref, and thus beyond the
scope of this study. The two younger glaciations, though, occurred both during
the last glacial cycle \mref. Indeed, the Cordilleran ice sheet did not keep
its maximum size during the entire glacial cycle. Instead, it is thought that,
for most of the last glacial cycle, ice cover was restricted to some of the
major mountain ranges of the Cordillera, while the maximum, ice-sheet stage,
corresponded to one or more short-lived expansion cycles.

The northern margin of the ice sheet suggests two such glacial episodes. The
first expansion cycle, the Gladstone glaciation, occurred at about 55-60\,ka,
during a local maximum of global ice volume on Earth known as the Marine
Isotope Stage (MIS)~4 \mref. However, evidence for the Gladstone glaciation has
not been found the southern part of the ice-covered region, making it difficult
to seize its magnitude. The second expansion cycle, the McConnell glaciation,
was dated at 18\,ka, which corresponds to the last global ice volume maximum
(MIS~2). In opposite to the Gladstone glaciation, the McConnell glaciation has
been correlated to a contemporaneous glacier advance of the southern margin,
known as the Fraser glaciation, and dated at 17\,ka. Although a slight
difference in timing may exists between the timing of maximum extent of the
northern and southern ice margins, the The McConnell and Fraser glaciation
correspond to the same expansion cycle, which resulted in the Last Glacial
Maximum (LGM) extent of the Cordilleran ice sheet. This is the period where
most geological observations point at.

>>>>

In the northern sector of the ice sheet, at least four glaciations have been
identified
    \citep{Duk-Rodkin.1999, Ward.etal.2007, Ward.etal.2008,
           Briner.Kaufman.2008, Demuro.etal.2012,
           Stroeven.etal.2010, Stroeven.etal.2014}.
The two older episodes, often referred to as Reid
and pre-Reid, are older than the last glacial cycle, and thus beyond the
scope of this study. The two younger glaciations, though, occurred both during
the last glacial cycle. Indeed, the Cordilleran ice sheet did not keep
its maximum size during the entire glacial cycle. Instead, it is thought that,
for most of the last glacial cycle, ice cover was restricted to some of the
major mountain ranges of the Cordillera, while the maximum, ice-sheet stage,
corresponded to one or more short-lived expansion cycles.

The northern margin of the ice sheet suggests two such glacial episodes. The
first expansion cycle, the Gladstone glaciation, reached its maximum between
$50.4\pm3.0$ and $54.3\pm2.0$\,\unit{^{10}Be\,ka} \citep{Ward.etal.2007},
during a local maximum of global ice volume on Earth known as the Marine
Isotope Stage (MIS)~4. However, evidence for the Gladstone glaciation has
not been found the southern part of the ice-covered region, making it difficult
to seize its magnitude. The second expansion cycle, the McConnell glaciation,
built end moraines with oldest minimum apparent exposure ages of
$15.7\pm1.5$ and $17.7\pm1.6$\,\unit{^{10}Be\,ka} \citep{Stroeven.etal.2014},
which corresponds to the last global ice volume maximum
(MIS~2). In opposite to the Gladstone glaciation, the McConnell glaciation has
been correlated to a contemporaneous glacier advance of the southern margin,
known as the Fraser glaciation, with a maximum extent framed between
$17.4$ and $16.4$\,\unit{^{14}C\,cal\,ka} \citep[Fig.~4]{Porter.Swanson.1998}.
Within errors inherent to the dating methods \citep{Heyman.etal.2011}, the
McConnell and Fraser glaciation correspond to the same glacial episode, which
resulted in the Last Glacial Maximum (LGM) extent of the Cordilleran ice sheet.
This is the period where most geological observations point at.
